Introductory statistics with `intRo`

### 2016-02-19 jcgs-paper-2016/paper.Rmd
references + section titles

Upon the release of RStudio's Shiny [@shiny] it became easier for an R-based analysis to be converted to an interactive web application. This in turn led us to create an introductory statistics application which we call `intRo`, available at http://www.intro-stats.com. `intRo` offers a number of key advantages over traditional statistics software, including ease of use and an aim to foster student interest in coding. Additionally, `intRo` stands apart from new tools in that it is a supplement to an existing class, fully usable by a beginning statistics student. These advantages will be discussed at length in this text.

@@

# Using intRo

## intRo Package

@@

# Understanding intRo

>>>>

Upon the release of RStudio's Shiny [@shiny] it became easier for an R-based analysis to be converted to an interactive web application. This in turn led us to create an introductory statistics application which we call `intRo`, available at http://www.intro-stats.com. `intRo` offers a number of key advantages over traditional statistics software, including ease of use and an aim to foster student interest in coding. Additionally, `intRo` stands apart from new tools in that it is a supplement to an existing class, fully usable by a beginning statistics student. These advantages will be discussed at length in this text. The paper is structured as follows: section \ref{what-is-intro} introduces the application, its features and its usability. Section \ref{using-intro} describes the process of creating a classroom instance of `intRo` tailored to the individual instructor. Section \ref{understanding-intro} provides technical details on the implementation of `intRo`. Finally, Section \ref{conclusions-and-future-work} discusses some future possibilities and limitations of the software.

@@

# Using `intRo`

## `intRo` Package

@@

# Understanding `intRo`
